\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-04 article.tex
Added outline and moved around the sections

@@

% Make title bold
\title{\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche}

% Single author
\author{Bjorn Michelsen, III. Dan \\
  \texttt{<bjorn@bmichelsen.no>} \\
  \\
  ITF Tromsdalen School of Taekwon-Do \\
  Tromso, Norway
  }

@@

\section*{\centering Abstract}
\begin{em}
  Patterns in International Taekwon-Do Federation (ITF) are defined as a
  choreographed sequence of fundamental movements, which represents an attack
  or defense towards a particular target area or definite action of an
  attacker, against one or several imaginary opponents.

@@

  A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
  of uncovering whether or not there is a bias to either arm, is reported here.
\end{em}

% Method
%   - Approach
%   - Collecting data
%   - Analysis of data
%   - Uncertainty
% Results
%   - Tables
%   - Graphs
% Conclusions

%Problem definition
%Is there a bias towards the right or the left arm in ITF Taekwon-Do
%patterns Chon-Ji to Juche?

\Section{Introduction}
A \emph{pattern} is a series of predefined basic elements called fundamental
movements. The \emph{fundamental movements} are attack or defensive techniques
against a specific target area or a predetermined action of an attacker.

@@

% incorporate the problem statement within the Introduction instead of using
% its own subsection

\SubSection{Problem Statement}
% pp. 154-155
% given the weight/importance of fundamental movements and patterns in the encyclopedia
% with approximately 3,200 techniques and
%Patterns, therefore,
%are the technical identity of Taekwon-Do.
% The following points should be considered while performing patterns:
%
%   9. Attack and defense techniques should be equally
%      distributed among right and left hands and feet
%
% and
%
% 'using every available attacking and blocking tool from different
% directions..'
%
% and the recent discovery of the right leg bias,
%
% note that Gibb's article includes *all* the patterns

@@

@@

% Unnumbered section (note the asteriks)
\section*{Acknowledgments}

Thank you, thank you, thank you!

>>>>

% Introduction
%   Definitions
%     Patterns
%     Fundamental movements
%     Groups of techniques
%       blocks
%       strikes
%       thrusts
%       punches
%     Tagging
%  Problem statement

% Method
%   Approach
%   Collecting data
%   Analysis of data
%   Tagging
%     Group of tags || Kind of Tags
%       height
%       weapon
%       type etc.
%    Difficulties related to tagging
%  Uncertainty
%
% Results
%   Tables
%   Graphs
% Conclusion

%Related work
%  Right Leg Bias

@@

% Make the title bold
\title{\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche}

% Author information
\author{Bjorn Michelsen, III. Dan \\
  \texttt{<bjorn@bmichelsen.no>} \\
  \\
  ITF Tromsdalen School of Taekwon-Do \\
  Tromso, Norway
  }

@@

\section*{\centering Abstract}
\begin{em}

%An academic abstract typically outlines four elements germane to the completed work:

    %* The research focus (i.e. statement of the problem(s)/research issue(s) addressed);
    %* The research methods used (experimental research, case studies, questionnaires, etc.);
    %* The results/findings of the research; and
    %* The main conclusions and recommendations

  % see the article: The Structure of Collaborative Tagging Systems
  % located in ~/tmp/tags.pdf

  Todo.
\end{em}

The Left Arm Bias in Taekwon-Do Patterns Chon-Ji to Juche

\Section{Introduction}

Patterns in International Taekwon-Do Federation (ITF) are defined as a
choreographed sequence of fundamental movements, which represents an attack
or defense towards a particular target area or definite action of an
attacker, against one or several imaginary opponents.

@@

A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
of uncovering whether or not there is a bias to either arm, is reported here.

A \emph{pattern} is a series of predefined basic elements called fundamental
movements. The \emph{fundamental movements} are attack or defensive techniques
against a specific target area or a predetermined action of an attacker.

@@

% Problem Statement
%
% pp. 154-155
% given the weight/importance of fundamental movements and patterns in the encyclopedia
% with approximately 3,200 techniques and
%Patterns, therefore,
%are the technical identity of Taekwon-Do.
% The following points should be considered while performing patterns:
%
%   9. Attack and defense techniques should be equally
%      distributed among right and left hands and feet
%
% and
%
% 'using every available attacking and blocking tool from different
% directions..'
%
% and the recent discovery of the right leg bias,
%
% Is there a bias towards the right or the left arm in ITF Taekwon-Do
% patterns Chon-Ji to Juche?
%
% note that Gibb's article includes *all* the patterns

@@

% Tagging can be defined as the practice of creating and
% managing labels that categorize content using simple
% keywords.

@@

% Unnumbered section (note the '*')
\section*{Acknowledgments}

  Todo.
